### 2019-10-11 source/cadabra/dGamma.tex
Minor housekeeping. No major changes.
Fixed a few typos in some of the tex and sh files.

Here we impose the RNC conition by setting the $\Gamma^{a}{}_{bc}$ to zero (but not their derivatives).

@@

% =================================================================================================
\section*{Stage 3: Replace partial derivatives $\Gamma$ with partial derivatives $R$}

>>>>

Here we impose the RNC condition by setting the $\Gamma^{a}{}_{bc}$ to zero (but not their derivatives).

@@

% =================================================================================================
\section*{Stage 3: Replace partial derivatives of $\Gamma$ with partial derivatives of $R$}
